Machine Learning, Physics, and Equilibrium (proposed title)

### 2019-05-10 distill_draft_notes/Draft/Draft.tex
starting to clarify connections between training and equilibrium (wip)

\begin{document}
\title{Physics of Equilibrium}
\author{Patrick, Juan-Miguel, Arthur, Peter, Nathan}
\maketitle

@@

>>>>

\begin{document}
\title{Machine Learning, Physics, and Equilibrium (proposed title)}
\author{Patrick, Juan-Miguel, Peter, Nathan}
\maketitle

@@

\section{Connecting training with equilibrium}

Machine learning with energy-based models bears some strong resemblance to long-studied subfields of physics. For instance, in machine learning we want to model systems which could have (exponentially) many possible configurations using only a small set of parameters. A similar approach is used in the study of statistical physics and thermodynamics, where we describe thermodynamic systems by an energy function (sometimes referred to as a potential) which consists of a very small set of parameters (temperature, pressure, etc.). If two systems, with different values of these parameters, are allowed to interact, energy will flow -- in both directions -- between them . This energy exchange process causes the system's thermodynamic parameters to change values. As we all know, putting food in the oven -- whose temperature is typically very hot -- will cause the food to heat up. Leaving hot food out in the kitchen will cause it to cool down again.
